lnc34a splice junctions

### 2017-11-12 inst/lnc34aSplJnc/lnc34aSplJnc.Rmd
reran lnc34aSplJnc.Rmd with new rds file and new download method
more accurate counting of splJnc reads in analysis

#splice junctions
load('/Users/jasonserviss/Github/miR34a_asRNA_project/data/lnc34aSpliceJncs.rda')
splJnc <- .
rm(.)

splJnc <- splJnc %>%
  mutate(
    cellline = gsub(".*LongRnaSeq(.*)Cell.*", "\\1", filename),
    feature = "splice junction",
    tag = paste(cellline, feature, sep = "-"),
    gene = "NA"
  ) %>%
  select(cellline, feature, start, stop, tag) %>%
  group_by(start, stop) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(y = 1:length(.data$n))
```

@@

##splice junctions
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = splJnc,
    aes(xmin = start, xmax = stop, y = y, fill = n),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  viridis::scale_fill_viridis() +
  ggthemes::theme_few() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Splice junctions") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(title = "n reads", title.position = "top", title.hjust = 0.5))

>>>>

#splice junctions
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "lnc34aSpliceJncs.rds"
splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

splJnc <- splJnc %>%
  mutate(cellline = gsub(".*LongRnaSeq(.*)Cell.*", "\\1", filename)) %>%
  select(cellline, start, stop, score2) %>%
  group_by(start, stop) %>%
  summarize(n = sum(score2)) %>%
  ungroup() %>%
  filter(n > 2) %>%
  arrange(desc(n)) %>%
  mutate(y = 1:length(.data$n))
```

@@

##splice junctions
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = splJnc,
    aes(xmin = start, xmax = stop, y = y, fill = n),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(1, "mm"),
    colour = "gray"
  ) +
  viridis::scale_fill_viridis() +
  ggthemes::theme_few() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Splice junctions") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(title = "n reads", title.position = "top", title.hjust = 0.5))
